An Architecture for Real-Time Location Recommendation for Field Data Collection

### 2017-03-30 Dynamic Enumerator Allocation/Paper/v3.b/Paper.tex
Update paper

@@

\begin{figure}[!]
	\centering
	\includegraphics[width=8cm]{Resources/Images/client-algorithm-nornal-global}
	\caption{The flowchart of experiment scenario}
	\label{fig:client-algorithm-nornal-global}
\end{figure}

These two data are tested using the proposed program, which combines Publish/Subscribe mechanism and CoEAs. The scenario used in testing is shown in the flowchart in \autoref{fig:client-algorithm-nornal-global}. The output of this test is compared against the output from the benchmark program that uses CoEAs algorithms only. Both programs output the routes for each vehicle which can be illustrated as follows:

>>>>

In the math formula \cite{kulkarni_integer_1985}, binary variables $x_{ijk}$ are equal to $1$ when vehicle $k$ visits node $j$ immediately after node $i$. Auxiliary variable $y_i$ is also used in the subtour elimination constraints to indicate whether the route $i$ is used in the solution. \\

Minimize
\begin{flalign}
\label{eq:1}
\sum_{i=1}^{N+M}\sum_{j=1}^{N+M}\sum_{k=1}^{K}c_{ij}x_{ijk};
\end{flalign}

Subject to:
\begin{flalign}
\label{eq:2}
\sum_{i=1}^{N+M}\sum_{k=1}^{K}x_{ijk} = 1  (j=1,..., N);
\end{flalign}

\begin{flalign}
\label{eq:3}
\sum_{j=1}^{N+M}\sum_{k=1}^{K}x_{ijk} = 1  (j=1,..., N);
\end{flalign}

\begin{flalign}
\label{eq:4}
&\sum_{i=1}^{N+M}x_{ihk} - \sum_{j=1}^{N+M}x_{hjk} = 0 \\
\nonumber
&(k=1,...,K; h=1,...,N+M);
\end{flalign}

\begin{flalign}
\label{eq:5}
\sum_{i=1}^{N+M} \sum_{j=1}^{N+M} d_ix_{ijk} \leq Q (k=1,...,K);
\end{flalign}

\begin{flalign}
\label{eq:6}
\sum_{i=1}^{N+M} \sum_{j=1}^{N+M} (c_{ij}w_{ij} + t_i) x_{ijk} \leq T (k=1,...,K);
\end{flalign}

\begin{flalign}
\label{eq:7}
\sum_{i=N+1}^{N+M} \sum_{j=1}^{N} x_{ijk} \leq 1 (k=1,...,K);
\end{flalign}

\begin{flalign}
\label{eq:8}
\sum_{j=N+1}^{N+M} \sum_{i=1}^{N} x_{ijk} \leq 1 (k=1,...,K);
\end{flalign}

\begin{flalign}
\label{eq:9}
&y_i - y_j + (M + N)x_{ijk} \leq N + M - 1; \\
\nonumber
&for 1 \leq i \neq j \leq N and 1 \leq k \leq K;
\end{flalign}

\begin{flalign}
\label{eq:10}
x_{ijk} \in \{0, 1\} \forall i,j,k;
\end{flalign}

\begin{flalign}
\label{eq:11}
y_i \in \{0,1\} \forall i;
\end{flalign}

The objective \ref{eq:1} minimizes the total cost. Constraints \ref{eq:2} and \ref{eq:3} guarantee that each customer is served by exactly one vehicle. The flow conservation is guaranteed through constraint \ref{eq:4}. Vehicle capacity and route duration constraints are found in \ref{eq:5} and \ref{eq:6}, respectively. Constraints \ref{eq:7} and \ref{eq:8} check vehicle availability. Subtour elimination constraints are in \ref{eq:9}. Finally, \ref{eq:10} and \ref{eq:11} define x and y as binary variables.

@@

These two data are tested using the proposed program, which combines Publish/Subscribe mechanism and CoEAs. The output of this test is compared against the output from the benchmark program that uses CoEAs algorithms only. Both programs output the routes for each vehicle which can be illustrated as follows:

### 2017-03-30 Dynamic Enumerator Allocation/Paper/v4/Paper.tex
Update paper

% *** SUBFIGURE PACKAGES ***
\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

@@

%-----------------------------------------------------------------------------%
\section{Related Works}
\label{sec:related-works}
%-----------------------------------------------------------------------------%
%-----------------------------------------------------------------------------%
\subsection{Multi-Depot Vehicle Routing Problem (MDVRP)}
\label{ssec:mdvrp}
%-----------------------------------------------------------------------------%
VRP is an optimization problem that focused on the query: \textit{`given a set of vehicles and a starting point (depot), find the best route to visit all customers'}. In cases there is more than one depot, VRP is known as MDVRP \cite{montoya-torres_literature_2015}. \autoref{fig:mdvrp-illustration} shows an example of an MDVRP solution that uses two depots and two routes that associate with each depot. Basically, a solution for MDVRP is a set of routes such that: (i) each route starts and ends at the same depot, (ii) each customer is only served once by one vehicle, (iii) the total demand on each route does not exceed vehicle's capacity, (iv) the maximum route time is satisfied, and (v) the total cost is minimized.

@@

According to Renaud et al \cite{renaud_tabu_1996}, the MDVRP can be formally described as follows:
\begin{enumerate}
	\item Let $G = (V, A)$ be a complete graph, where $V$ is the set of nodes and $A$ is the set of arcs. 
	\item Partition the nodes into two subsets: the customers to serve $V_C$ = \{1,..., $N$\} and the depots $V_D$ = \{$N$+1,..., $N+M$\}, with $V_C \cup V_D$ = $V$ and $V_C \cap V_D$ = $\oslash$. 
	\item There is a non-negative cost $c_{ij}$ associated with each arc $(i, j) \in A$. 
	\item The demand of each customer is $d_i$ (there is no demand at the depot nodes).
	\item There is also a fleet of $K$ identical vehicles, each with capacity $Q$.
	\item The service time at each customer $i$ is $t_i$ while the maximum route duration time is set to $T$.
	\item A conversion factor $w_{ij}$ might be needed to transform the cost $c_{ij}$ into time units. In the classical MDVRP, however, the cost is similar with the time and distance units. Hence, $w_{ij}$ = $1$.
\end{enumerate}

%-----------------------------------------------------------------------------%
\subsection{Evolution Algorithms (EAs)}
\label{ssec:evolution-algorithms}
%-----------------------------------------------------------------------------%
Evolution Algorithms (EAs) is an optimization algorithm inspired by nature. EAs involve selection and reproduction processes to purify population from the solution candidates. According to Engelbrecht \cite{engelbrecht_coevolution_2007}, the EAs lifecycle begins with randomly configuring the initial population. For each iteration, every individual in the population is evaluated using an objective function to find the solution candidates. Each solution candidate is labeled with a fitness value based on its evaluation result. These candidates will then reproduce and create the next generation. The whole process will be repeated using the new-generation individuals. The iteration will stop once it hits a certain time limit, which is 60 seconds.

In standard EAs, evolution is usually viewed as the population's attempts to adapt in a fixed physical environment. Furthermore, Coevolutionary algorithms (CoEAs), a development of EAs, realize that in natural evolution the physical environment is influenced by other independently-acting biological populations \cite{engelbrecht_coevolution_2007}. Based on the interaction of each species, CoEAs can be distinguished into two categories: competitive and cooperative \cite{engelbrecht_coevolution_2007}. In the competitive coevolution, each individual competes with other individuals in the same group. Meanwhile, the cooperative coevolution has its species mutually interacted or, at least, not harming each other.

%-----------------------------------------------------------------------------%
\subsection{Publish/Subscribe Paradigm}
\label{ssec:pub-sub}
%-----------------------------------------------------------------------------%
The publish/subscribe interaction is a communication method between client and server, which involves subscribers as clients. The subscribers are the parties who have interests in a certain event or the pattern of an event. These subscribers will get a notification from the publisher about the event they are interested in \cite{eugster_many_2003}.

The basic model of the publish/subscribe system, as can be seen in \autoref{fig:pub-sub-general}, depends on the event notification service that provides storage and management of subscription. This event service acts as a mediator between the publisher (the event's producer) and the subscriber (the event's consumer).

\begin{figure}[!]
	\centering
	\includegraphics[width=8cm]{Resources/Images/pub-sub-general}
	\caption{Basic architecture in Publish/Subscribe Mechanism \cite{eugster_many_2003}}
	\label{fig:pub-sub-general}
\end{figure}

One of the benefits of using publish/subscribe mechanism is the loose coupling characteristic \cite{eugster_many_2003} between the publisher and the subscriber. The separation of information (decoupling) between publisher and subscriber can be divided into 3 (three) dimensions, which are:

\begin{enumerate}
	\item Space decoupling. \\
	During the interaction, publisher and subscriber do not need to know each other. The publisher sends an event and subscriber indirectly receives the event through the event service. The publisher does not hold any reference towards the subscriber and vice versa. 
	\item Time decoupling. \\
	The parties who are involved in the interactions do not have to interact in the same time. The publisher can send the event while in a disconnected state. Similarly, the subscriber can still receive the event, albeit disconnected. 
	\item Synchronizing decoupling. \\
	Publisher will not be blocked during the event producing. The subscriber can still obtain information despite, at the same time, working on other tasks. Publisher and subscriber are not in the main flow, hence not interacting synchronously. 
\end{enumerate}

@@

%-----------------------------------------------------------------------------%
\subsection{VRP Solver}
\label{ssec:vrp-solver}
%-----------------------------------------------------------------------------%
VRP solver is a module used for finding the best route/solution to visit all customers (census/survey locations) in a VRP/MDVRP. VRP solver is called in each thread in the thread pool (\autoref{alg:vrp-worker}). There are several algorithms that can be adopted to find the solution such as tabu search \cite{cordeau_tabu_1997}, adaptive large neighborhood search  \cite{pisinger_general_2007}, fuzzy logic guided genetic algorithm \cite{lau_application_2010}, paralel iterated tabu search \cite{cordeau_parallel_2012}, hybrid algorithm combining iterated local search and set partitioning \cite{subramanian_hybrid_2013}, hybrid genetic algorithm with adaptive diversity control \cite{vidal_implicit_2014}, hybrid granular tabu search \cite{escobar_hybrid_2014}, and cooperative coevolution algorithms (CoEAs) \cite{de_oliveira_cooperative_2016}. In this research, VRP solver utilizes CoEAs since CoEAs generates a competitive \textit{mean solution values} with relatively low CPU time compared to other algorithms \cite{de_oliveira_cooperative_2016}.

@@

%-----------------------------------------------------------------------------%
\section{Result}
\label{sec:testing}
%-----------------------------------------------------------------------------%
The performance of the proposed system is assessed through a number of experiments. This experiment uses 2 (two) input data: Cordeau's data and real administrative data. The service time for these two data is randomly generated by following the normal distribution.

@@

\begin{figure}[!]
	\centering
	\includegraphics[width=8cm]{Resources/Images/client-algorithm-nornal-global}
	\caption{The flowchart of experiment scenario}
	\label{fig:client-algorithm-nornal-global}
\end{figure}

These two data are tested using the proposed program, which combines Publish/Subscribe mechanism and CoEAs. The scenario used in testing is shown in the flowchart in \autoref{fig:client-algorithm-nornal-global}. The output of this test is compared against the output from the benchmark program that uses CoEAs algorithms only. Both programs output the routes for each vehicle which can be illustrated as follows:

@@

The test using Cordeau's data in normal condition shows that the pre-calculated routes generated by benchmark program yield a smaller total time (1,165,513.28 seconds) compared with that of the proposed program (1,165,706.84 seconds). However, the benchmark program has, a bigger standard deviation of 98,268.51 seconds, in contrast with the proposed program of 12997.91 seconds (\autoref{tbl:test_result_normal_cordeau_comparison}).

Similarly, the test using real administrative data in normal condition gives the result that pre-calculated routes from benchmark program return a smaller total time, yet a higher standard deviation compared with that of the proposed program. The benchmark program outputs a total time of 4,448,989.67 seconds and standard deviation of 119,720.84 seconds, while the proposed program gives total time of 4,559,658.67 seconds and standard deviation of 34,472.12 seconds (\autoref{tbl:test_result_normal_field_comparison}).

\begin{table}
	\centering
	\ra{1.3}
	\caption{The comparison between CoEAs algorithm and Pub/Sub + CoEAs algorithm for the Cordeau data}
	\label{tbl:test_result_normal_cordeau_comparison}
	\begin{tabular}{lrr}
		\toprule
		Units & CoEAs & CoEAs + Pub/Sub\\ 
		\midrule
		Total time (s) & 1165513.28 & 1165706.84\\
		Mean of time (s) & 291378.32 & 291426.71\\
		Std. Dev of time (s) & 98268.51 & 12997.91\\
		\bottomrule
	\end{tabular}
\end{table}

\begin{table}
	\centering
	\ra{1.3}
	\caption{The comparison between CoEAs algorithm and Pub/Sub + CoEAs algorithm for the real field data}
	\label{tbl:test_result_normal_field_comparison}
	\begin{tabular}{lrr}
		\toprule
		Units & CoEAs & CoEAs + Pub/Sub\\ 
		\midrule
		Total time (s) & 4448989.67 & 4559658.67\\
		Mean of time (s) & 296599.31 & 303977.24\\
		Std. Dev of time (s) & 119720.84 & 34472.12\\
		\bottomrule
	\end{tabular}
\end{table}

%-----------------------------------------------------------------------------%
\section{Conclusion and Future Works}
\label{sec:conclusion-future-works}
%-----------------------------------------------------------------------------%
This paper proposes the use of Cooperative Coevolutionary Algorithm (CoEAs) combined with Publish/Subscribe mechanism to solve the real-time location recommendation problem in field data collection. Based on the test results, it is concluded that:

\begin{enumerate}
	\item CoEAs algorithm outputs a more efficient route based on the total cost point of view, but, 
	\item The CoEAs algorithm cannot be directly used in census/survey location recommendation since it contains a huge standard deviation of the total cost for each route, thus, 
	\item The use of a real-time mechanism such as Publish/Subscribe mechanism is needed to overcome the inequality problem between each route. It means the tasks and locations will be more evenly distributed and every enumerator has equal workloads.
\end{enumerate}

Publish/Subscribe mechanism is not the only option that can be used to develop a real-time system. Further studies using other mechanisms such as Push/Pull mechanism and Request/Reply mechanism is required for comparison. A research on analyzing the performance of each mechanism in varying network conditions are also necessary to create a simulation of real field conditions.

>>>>

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig
\usepackage{subcaption}

@@

%-----------------------------------------------------------------------------%
\section{Related Works}
\label{sec:related-works}
%-----------------------------------------------------------------------------%

%-----------------------------------------------------------------------------%
\subsection{Coevolution Algorithms (CoEAs) MDVRP}
\label{ssec:evolution-algorithms}
%-----------------------------------------------------------------------------%
VRP is an optimization problem that focused on the query: \textit{`given a set of vehicles and a starting point (depot), find the best route to visit all customers'}. In cases there is more than one depot, VRP is known as MDVRP \cite{montoya-torres_literature_2015}. \autoref{fig:mdvrp-illustration} shows an example of an MDVRP solution that uses two depots and two routes that associate with each depot. Basically, a solution for MDVRP is a set of routes such that: (i) each route starts and ends at the same depot, (ii) each customer is only served once by one vehicle, (iii) the total demand on each route does not exceed vehicle's capacity, (iv) the maximum route time is satisfied, and (v) the total cost is minimized.

@@

Coevolutionary algorithms (CoEAs) is one of many algorithms \cite{cordeau_tabu_1997} \cite{pisinger_general_2007} \cite{lau_application_2010} \cite{cordeau_parallel_2012} \cite{subramanian_hybrid_2013} \cite{vidal_implicit_2014} \cite{escobar_hybrid_2014} \cite{de_oliveira_cooperative_2016} that can be used to solve MDVRP. CoEAs realize that in natural evolution the physical environment is influenced by other independently-acting biological populations \cite{engelbrecht_coevolution_2007}. Based on the interaction of each species, CoEAs can be distinguished into two categories: competitive and cooperative \cite{engelbrecht_coevolution_2007}. In the competitive coevolution, each individual competes with other individuals in the same group. Meanwhile, the cooperative coevolution has its species mutually interacted or, at least, not harming each other.

Penggunaan CoEAs untuk menyelesaikan MDVRP telah diteliti oleh beberapa peneliti, salah satunya adalah de Oliveira et al. \cite{de_oliveira_cooperative_2016}. Pada algoritma usulan de Oliveira et al., terdapat 2 (dua) tahap, yaitu inisiasi populasi dan population evolution. Pada tahap inisiasi, populasi dibangun dengan menggunakan Nearest Insertion Heuristic (NIH) dan semi-greedy berbasis NIH. Tahap population evolution menggunakan paralel module dan monitor module. Paralel module terdiri dari 3 (tiga) modules, yaitu: Population Evolve (PE), Complete Solution Evaluate (CSE), dan Elite Group (EG) module. Sementara monitor module melakukan monitoring proses yang terjadi pada paralel module. Arsitektur usulan de Oliveira et al. digambarkan pada \autoref{fig:coes_paralel_modules}.

\begin{figure}[!]
	\centering
	\includegraphics[width=6cm]{Resources/Images/coes_paralel_modules}
	\caption{Architecture of Parallel Modules \cite{de_oliveira_cooperative_2016}}
	\label{fig:coes_paralel_modules}
\end{figure}

%-----------------------------------------------------------------------------%
\subsection{Publish/Subscribe Paradigm}
\label{ssec:pub-sub}
%-----------------------------------------------------------------------------%
The publish/subscribe interaction is a communication method between client and server, which involves subscribers as clients. The subscribers are the parties who have interests in a certain event or the pattern of an event. These subscribers will get a notification about the event they are interested in \cite{eugster_many_2003}. One of the benefits of using publish/subscribe mechanism is the loose coupling characteristic \cite{eugster_many_2003} between the publisher and the subscriber.

The basic model of the publish/subscribe system depends on the event notification service that provides storage and management of subscription. This event service acts as a mediator between the publisher (the event's producer) and the subscriber (the event's consumer).

@@

%-----------------------------------------------------------------------------%
\subsection{VRP Solver}
\label{ssec:vrp-solver}
%-----------------------------------------------------------------------------%
VRP solver is a module used for finding the best route/solution to visit all customers (census/survey locations). VRP solver is called in each thread in the thread pool (\autoref{alg:vrp-worker}). In this research, VRP solver utilizes CoEAs since CoEAs generates a competitive \textit{mean solution values} with relatively low CPU time compared to other algorithms \cite{de_oliveira_cooperative_2016}.

@@

%-----------------------------------------------------------------------------%
\section{Result}
\label{sec:testing}
%-----------------------------------------------------------------------------%
Masing-masing komponen pada sistem diimplementasikan dengan cara yang berbeda-beda. Recommendation publisher diimplementasikan dalam bahasa pemrograman Java, dan dicompile dengan compiler java 1.8.0\_121. VRP Solver yang dibangun berdasarkan algoritma CoEAs diimplementasikan dalam bahasa pemrograman C++, dan dicompile dengan compiler c++ 5.4.0 20160609. Sementara message broker diimplementasikan menggunakan redis cluster 3.2.6 dengan 6 nodes, 3 nodes sebagai master dan 3 nodes sebagai slave.

Seluruh komponen kemudian dikombinasikan dan dijalankan under the environment of Quad-Core Intel® Core™ i3-4030U CPU @ 1.90GHz, 3,7 GiB RAM and Elementary OS Loki 64bit operating system. Sementara masing-masing redis node dijalankan sebagai Docker container under the environment of Quad-Core Intel® Core™ i3-4030U CPU @ 1.90GHz, 3,7 GiB RAM and Debian Jessie 64bit operating system.

Sebuah aplikasi client dirancang untuk mensimulasikan kondisi sebenarnya. Langkah-langkah yang dijalankan pada client, as shown in the flowchart in \autoref{fig:client-algorithm-nornal-global}, adalah sebagai berikut:

\begin{enumerate}
	\item Client melakukan subscription dengan menggunakan current location-nya sebagai topik,
	\item Client menunggu sampai server (publisher) memberikan respon berupa next-location yang harus dikunjungi, 
	\item Client melakukan traveling ke next-location, 
	\item Client melakukan pencacahan, 
	\item Client secara asyncronous men-set current location-nya pada shared memory
\end{enumerate}

This experiment uses 2 (two) input data: Cordeau's data and real administrative data. The service time for these two data is randomly generated by following the normal distribution, based on Sudman \cite{sudman_time_1965}. Input data yang digunakan adalah sebagai berikut:

@@

\begin{figure}[!]
	\centering
	\includegraphics[width=8cm]{Resources/Images/client-algorithm-nornal-global}
	\caption{The flowchart of client application}
	\label{fig:client-algorithm-nornal-global}
\end{figure}

These two data are tested using the proposed program, which combines Publish/Subscribe mechanism and CoEAs. The output of this test is compared against the output from the benchmark program that uses CoEAs algorithms only. Both programs output the routes for each vehicle which can be illustrated as follows:

@@

Figure \autoref{fig:test_result_normal_cordeau_comparison} shows the routes generated by benchmark program (\autoref{fig:test_result_normal_cordeau_coes_paper}) and proposed program (\autoref{fig:test_result_normal_cordeau_pubsub_coes_paper}) using Cordeau's data in normal condition. The test result, as can be seen in \autoref{tbl:test_result_normal_cordeau_comparison}, shows that the pre-calculated routes generated by benchmark program yield 0.029 percent smaller in total time (905,018.39 seconds) compared with that of the proposed program (905,281.55 seconds). However, the benchmark program has standard deviation of 49,715.99 seconds, or more than 2 times bigger than the proposed program of 15,496.22 seconds.

\begin{table}[!]
	\centering
	\ra{1.3}
	\caption{The comparison between CoEAs algorithm and Pub/Sub + CoEAs algorithm for the Cordeau data}
	\label{tbl:test_result_normal_cordeau_comparison}
	\begin{tabular}{lrr}
		\toprule
		Units & CoEAs & CoEAs + Pub/Sub\\ 
		\midrule
		Total time (s) & \textbf{905,018.39} & 905,281.55\\
		Mean of time (s) & \textbf{226,254.60} & 226,320.39\\
		Std. Dev of time (s) & 49,715.99 & \textbf{15,496.22}\\
		\bottomrule
	\end{tabular}
\end{table}

Similarly, the test using real administrative, as shown in \autoref{tbl:test_result_normal_field_comparison}, data in normal condition gives the result that pre-calculated routes from benchmark program return a smaller total time, yet a higher standard deviation compared with that of the proposed program. The benchmark program outputs a total time of 3,373,390.19 seconds and standard deviation of 91,123.23 seconds, while the proposed program gives total time of 3,676,718.19 seconds and standard deviation of 37,261.85 seconds. The proposed program gives result only 0.52 percent higher in total time but 59.1 percent or almost 3 times lower in standard deviation. \autoref{fig:test_result_normal_field_comparison} show the routes generated by benchmark program (\autoref{fig:test_result_normal_field_coes_paper}) and proposed program (\autoref{fig:test_result_normal_cordeau_pubsub_coes_paper}).

\begin{table}[!]
	\centering
	\ra{1.3}
	\caption{The comparison between CoEAs algorithm and Pub/Sub + CoEAs algorithm for the real field data}
	\label{tbl:test_result_normal_field_comparison}
	\begin{tabular}{lrr}
		\toprule
		Units & CoEAs & CoEAs + Pub/Sub\\ 
		\midrule
		Total time (s) & \textbf{3,373,390.19} & 3,676,718.19\\
		Mean of time (s) & \textbf{224,892.68} & 245,114.55\\
		Std. Dev of time (s) & 91,123.23 & \textbf{37,261.85}\\
		\bottomrule
	\end{tabular}
\end{table}

\begin{figure*}[!]
	\centering
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Resources/Images/test_result_normal_cordeau_coes_paper}
		\caption{CoEAs}
		\label{fig:test_result_normal_cordeau_coes_paper}
	\end{subfigure}%
	~ 
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Resources/Images/test_result_normal_cordeau_pubsub_coes_paper}
		\caption{Publish/Subscribe + CoEAs}
		\label{fig:test_result_normal_cordeau_pubsub_coes_paper}
	\end{subfigure}
	\caption{The comparison of routes between CoEAs algorithm and Pub/Sub + CoEAs algorithm for Cordeau data}
	\label{fig:test_result_normal_cordeau_comparison}
\end{figure*}

\begin{figure*}[!]
	\centering
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Resources/Images/test_result_normal_field_coes_paper}
		\caption{CoEAs}
		\label{fig:test_result_normal_field_coes_paper}
	\end{subfigure}%
	~ 
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Resources/Images/test_result_normal_field_pubsub_coes_paper}
		\caption{Publish/Subscribe + CoEAs}
		\label{fig:test_result_normal_field_pubsub_coes_paper}
	\end{subfigure}
	\caption{The comparison of routes between CoEAs algorithm and Pub/Sub + CoEAs algorithm for real field data}
	\label{fig:test_result_normal_field_comparison}
\end{figure*}

%-----------------------------------------------------------------------------%
\section{Conclusion and Future Works}
\label{sec:conclusion-future-works}
%-----------------------------------------------------------------------------%
Paper ini bertujuan untuk mencari solusi atas kelemahan dari CoEAS MDVRP ketika digunakan untuk menggenerate rekomendasi lokasi pencacahan dengan mengusulkan penggunaan mekanisme publish/subscribe. Arsitektur utama sistem usulan terdiri dari 2 (dua) komponen, yaitu publisher dan message broker, dimana pada publisher dijalankan VRP Solver yang mengadopsi algoritma CoEAs.

We evaluate the proposed system using 2 (two) kind of data, Coedeau's data and real administrative data. The experimental results shows that routes generated by proposed program are more prevalent in total route times compared with the pre-calculated routes produced by benchmark program.

Publish/Subscribe mechanism is not the only option that can be used to develop a real-time system. Further studies using other mechanisms such as Push/Pull and Request/Reply mechanism is required for comparison. A research on analyzing the performance of each mechanism in varying network conditions are also necessary to create a simulation of real field conditions.
